\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{casual}
\moderncvcolor{orange}

\usepackage[scale=0.75, top=2cm, bottom=3cm]{geometry}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage{ragged2e}
\usepackage{xcolor}


\usepackage[style=numeric,giveninits,maxbibnames=99,sorting=ydnt]{biblatex}

\addbibresource{Alexis-TOUMI.bib}
\defbibenvironment{bibliography}
  {\small \vspace{5pt} \list
     {\printtext[labelnumberwidth]{% label format from numeric.bbx
        \printfield{labelprefix}%
        \printfield{labelnumber}}}
     {\setlength{\topsep}{0pt}% layout parameters from moderncvstyleclassic.sty
      \setlength{\labelwidth}{\hintscolumnwidth}%
      \setlength{\labelsep}{\separatorcolumnwidth}%
      \leftmargin\labelwidth%
      \advance\leftmargin\labelsep}%
      \sloppy\clubpenalty4000\widowpenalty4000}
  {\endlist}
  {\item}

\usepackage{etoolbox}
\makeatletter
\patchcmd{\makecvhead} % <cmd>
  {\ifthenelse{\isundefined{\@email}}{}{\makenewline\emailsymbol\emaillink\textcolor{grey}{\@email}}} % <search>
  {\ifthenelse{\isundefined{\@email}}{}{\makenewline{\emailsymbol\textcolor{grey}\emaillink{\@email}}}%
  } % <replace>
  {}{} % <success><failure>
\makeatother

\name{\textbf{Alexis}}{\color{orange}\textbf{TOUMI}}


\AtBeginDocument{\hypersetup{
    pdftitle={CV-Alexis-TOUMI},
    colorlinks=true,
    urlcolor=orange,
    linkcolor=gray,
    citecolor=orange,
    pageanchor=false}}

\begin{document}

\makecvtitle

\vspace{-40pt}

{\centering
    \hypersetup{urlcolor=orange}
    \addresssymbol 127 avenue Jean Jaurès, 75019 Paris, France
    \hspace{25pt}
    \emailsymbol \href{mailto:alexis@toumi.email}{alexis@toumi.email}
    \hspace{25pt}
    \homepagesymbol \href{https://alexis.toumi.xyz}{alexis.toumi.xyz}
    \par}

\vspace{10pt}

\section{\textbf{EDUCATION}}

\cventry{2018 -- 2022}{D.Phil. Computer Science}{University of Oxford}{}{}{
\emph{Thesis:} \textbf{Category Theory for Quantum Natural Language Processing}, see \cite{DisCoPy,ToumiEtAl21,MeichanetzidisEtAl20a}.
\emph{Supervisors:} Prof.~Bob Coecke and Dr.~Dan Marsden.
\emph{Examiners:} Prof.~Sam Staton (University of Oxford) and Prof.~Dr.~Michael Moortgat (Utrecht University)
}

\cventry{2016 -- 2018}{M.Sc. Mathematics \& Computer Science}{University of Oxford}{}{Distinction}{
\emph{Thesis:} \textbf{Categorical Compositional Distributional Questions, Answers \& Discourse Analysis}, supervised by Prof.~Bob Coecke. This followed the publications \cite{CoeckeEtAl18a} and \cite{CoeckeEtAl18}.\linebreak
}

\cventry{2012 -- 2015}{B.Sc. Computer Science}{University of Oxford}{}{First-Class Honours}{
\emph{Thesis:} \textbf{Equilibrium Checking in Reactive Modules Games}, supervised by Prof.~Michael Wooldridge and Dr.~Julian Gutierrez. This was followed by two publications \cite{WooldridgeEtAl16} and \cite{ToumiEtAl15}.\linebreak
}

\vspace{-8pt}

\section{\textbf{AWARDS}}

\cventry{2018}{Oxford -- DeepMind Graduate Scholarship in Computer Science}{}{}{}{}
\cventry{2018}{Wolfson Harrison UK Research Council Quantum Foundation Scholarship}{}{}{}{}
\cventry{2013}{New College Academic Scholarship}{}{}{}{}


\section{\textbf{TEACHING}}

\cventry{2019}{Quantum Computer Science}{University of Oxford}{Class Tutor}{}{
String diagrams for quantum processes,
ZX-calculus, quantum foundations and algorithms.\linebreak
}\vspace{-4pt}
\cventry{2019}{Logic \& Proof}{University of Oxford}{Class Tutor}{}{
Propositional logic, SAT and constraint satisfaction, first-order logic and unification.\linebreak
}\vspace{-4pt}
\cventry{2018}{Computational Complexity}{University of Oxford}{Class Tutor}{}{
Turing machines and reductions, randomisation, introduction to descriptive complexity.\linebreak
}\vspace{-4pt}
\cventry{2018}{Data Science with Python}{ESILV Paris}{Teaching Assistant}{}{
Feature extraction from images, clustering, classification. Methodology for model evaluation.\linebreak
}\vspace{-4pt}

\vspace{-8pt}

\section{\textbf{WORK EXPERIENCE}}

\cventry{Oct 2022 --}{Post-doctoral researcher}
{Laboratoire d'Informatique \& Syst\`emes}{Marseille}{}{
Formal methods for quantum cellular automata and distributed quantum computing.
\linebreak
}\vspace{-4pt}

\cventry{2019 -- }{Research Scientist}
{Cambridge Quantum Computing}{Oxford}{part-time advisor}{
Natural language processing on noisy intermediate-scale quantum hardware, see \cite{
MeichanetzidisEtAl20a,
MeichanetzidisEtAl20}.\linebreak
Applied category theory for quantum computing and artificial intelligence, see \cite{ToumiEtAl21}.\linebreak
}\vspace{-4pt}

\cventry{May--Jul 2022}{General Manager}
{Le Lab Quantique}{Paris}{}{
Administration of a French nonprofit that promotes the emergence of quantum technologies.
\linebreak
}\vspace{-4pt}

\cventry{2017 -- 2018}{Data Scientist}{IRHT -- CNRS \& Teklia}{Paris}{}{Deep learning for the automated analysis of manuscripts from the Middle Ages, see \cite{BorosEtAl19}.\linebreak
}\vspace{-4pt}
\cventry{2015 -- 2016}{Machine Learning Engineer}{Tinyclues}{Paris}{Internship}{
Tensor factorisation on complex relational data: users, products, emails, clicks and sales.\linebreak
}\vspace{-4pt}

\cventry{2014 -- 2015}{Data Scientist}{Yonderlabs}{Berlin}{Internship}{
Probabilistic graphical models (HMM and CRF) applied to natural language processing.\linebreak
}

\vspace{-8pt}

\section{\textbf{LANGUAGES}}
\cvitem{Human}{Fluent in English and French. Basic German and beginner Arabic.}
\cvitem{Machine}{
I am the main developer of \href{https://discopy.org}{DisCoPy}
\cite{DisCoPy,ToumiEtAl22}, the Python library for computing with string diagrams.
Fluent: markdown, HTML, CSS.
Basic: Javascript, Haskell, SQL, C.\linebreak
}

\vspace{-8pt}

\nocite{*}

\printbibliography[title=\textbf{PUBLICATIONS}]

\end{document}
