\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{casual}
\moderncvcolor{red}

\usepackage[scale=0.75, top=2cm, bottom=3cm]{geometry}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage{ragged2e}
\usepackage{xcolor}


\usepackage[style=numeric,giveninits,maxbibnames=99,sorting=ydnt]{biblatex}

\addbibresource{Alexis-TOUMI.bib}
\defbibenvironment{bibliography}
  {\small \vspace{5pt} \list
     {\printtext[labelnumberwidth]{% label format from numeric.bbx
        \printfield{labelprefix}%
        \printfield{labelnumber}}}
     {\setlength{\topsep}{0pt}% layout parameters from moderncvstyleclassic.sty
      \setlength{\labelwidth}{\hintscolumnwidth}%
      \setlength{\labelsep}{\separatorcolumnwidth}%
      \leftmargin\labelwidth%
      \advance\leftmargin\labelsep}%
      \sloppy\clubpenalty4000\widowpenalty4000}
  {\endlist}
  {\item}

\usepackage{etoolbox}
\makeatletter
\patchcmd{\makecvhead} % <cmd>
  {\ifthenelse{\isundefined{\@email}}{}{\makenewline\emailsymbol\emaillink\textcolor{grey}{\@email}}} % <search>
  {\ifthenelse{\isundefined{\@email}}{}{\makenewline{\emailsymbol\textcolor{grey}\emaillink{\@email}}}%
  } % <replace>
  {}{} % <success><failure>
\makeatother


\name{\textbf{Alexis}}{\color{red}\textbf{TOUMI}}

\extrainfo{
\hypersetup{urlcolor=gray}
\mobilesymbol +33 7 52 93 77 99
\hspace{25pt}
\emailsymbol \href{mailto:alexis@toumi.email}{alexis@toumi.email}
\hspace{25pt}
\homepagesymbol \href{https://alexis.toumi.xyz}{alexis.toumi.xyz}}


\AtBeginDocument{\hypersetup{
    pdftitle={CV-Alexis-TOUMI},
    colorlinks=true,
    urlcolor=red,
    linkcolor=gray,
    citecolor=red,
    pageanchor=false}}

\begin{document}

\makecvtitle

\vspace{-30pt}

\section{\textbf{EDUCATION}}

\cventry{2018 -- 2022}{DPhil Computer Science}{University of Oxford}{}{}{
\emph{Thesis:} \textbf{Category Theory for Quantum Natural Language Processing},\linebreak supervised by Prof.~Bob Coecke and Dr.~Dan Marsden, see \cite{
QNLP-Eduardo,
language-games,
DisCoPy,
ToumiEtAl21,
CoeckeEtAl20,
functorial-question,
MeichanetzidisEtAl20a,
MeichanetzidisEtAl20,
ShieblerEtAl20,
McPheatEtAl21}.\linebreak
}

\cventry{2016 -- 2018}{MSc Mathematics \& Computer Science}{University of Oxford}{}{Distinction}{
\emph{Thesis:} \textbf{Categorical Compositional Distributional Questions, Answers \& Discourse Analysis}, supervised by Prof.~Bob Coecke. This followed the publications \cite{CoeckeEtAl18a} and \cite{CoeckeEtAl18}.\linebreak
}

\cventry{2012 -- 2015}{BSc Computer Science}{University of Oxford}{}{First-Class Honours}{
\emph{Thesis:} \textbf{Equilibrium Checking in Reactive Modules Games}, supervised by Prof.~Michael Wooldridge and Dr.~Julian Gutierrez. This was followed by two publications \cite{WooldridgeEtAl16} and \cite{ToumiEtAl15}.\linebreak
}


\section{\textbf{AWARDS}}

\cventry{2018}{Oxford -- DeepMind Graduate Scholarship in Computer Science}{}{}{}{}
\vspace{2pt}
\cventry{2018}{Wolfson Harrison UK Research Council Quantum Foundation Scholarship}{}{}{}{}
\vspace{2pt}
\cventry{2013}{New College Academic Scholarship}{}{}{}{}
\vspace{2pt}

\section{\textbf{TEACHING}}

\cventry{2019}{Quantum Computer Science}{University of Oxford}{Class Tutor}{}{
String diagrams for quantum processes,
ZX-calculus, quantum foundations and algorithms.\linebreak
}\vspace{-4pt}
\cventry{2019}{Logic \& Proof}{University of Oxford}{Class Tutor}{}{
Propositional logic, SAT and constraint satisfaction, first-order logic and unification.\linebreak
}\vspace{-4pt}
\cventry{2018}{Computational Complexity}{University of Oxford}{Class Tutor}{}{
Turing machines and reductions, randomisation, introduction to descriptive complexity.\linebreak
}\vspace{-4pt}
\cventry{2018}{Data Science with Python}{ESILV Paris}{Teaching Assistant}{}{
Feature extraction from images, clustering, classification. Methodology for model evaluation.\linebreak
}\vspace{-4pt}


\section{\textbf{INDUSTRY}}

\cventry{2022 -- }{General Manager}
{Le Lab Quantique}{Paris}{}{
Administration of a French nonprofit that promotes the emergence of quantum technologies.
\linebreak
}\vspace{-4pt}
\cventry{2019 -- }{Research Scientist}
{Cambridge Quantum Computing}{Oxford}{Part time}{
Natural language processing on noisy intermediate-scale quantum hardware, see \cite{
MeichanetzidisEtAl20a,
MeichanetzidisEtAl20}.\linebreak
Applied category theory for quantum computing and artificial intelligence, see \cite{ToumiEtAl21}.\linebreak
}\vspace{-4pt}
\cventry{2017 -- 2018}{Data Scientist}{IRHT -- CNRS \& Teklia}{Paris}{}{Deep learning for the automated analysis of manuscripts from the Middle Ages, see \cite{BorosEtAl19}.\linebreak
}\vspace{-4pt}
\cventry{2015 -- 2016}{Machine Learning Engineer}{Tinyclues}{Paris}{Internship}{
Tensor factorisation on complex relational data: users, products, emails, clicks and sales.\linebreak
}\vspace{-4pt}
\cventry{2014 -- 2015}{Data Scientist}{Yonderlabs}{Berlin}{Internship}{
Probabilistic graphical models (HMM and CRF) applied to natural language processing.\linebreak
}
\pagebreak

\printbibliography[title=\textbf{PUBLICATIONS}]

\vspace{11pt}

\section{\textbf{LANGUAGES}}
\cvitem{Human}{Fluent in English and French. Basic German and beginner Arabic.}
\cvitem{Machine}{
Advanced Python. Working knowledge of Haskell, Scala, C, SQL.\linebreak
I am the developer of \href{https://github.com/oxford-quantum-group/discopy}{DisCoPy}
\cite{DisCoPy,ToumiEtAl22}, the Python library for monoidal categories.\linebreak
}



\end{document}
