\documentclass[11pt,a4paper,sans,colorlinks=true]{moderncv}
\moderncvstyle{casual}
\moderncvcolor{orange}

\usepackage[scale=0.75, top=2cm, bottom=2cm]{geometry}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage{ragged2e}
\usepackage{xcolor}

\usepackage[style=numeric,giveninits,maxbibnames=99,sorting=ydnt]{biblatex}

\addbibresource{CV-selection.bib}

\defbibenvironment{bibliography}
  {\small \vspace{5pt} \list
     {\printtext[labelnumberwidth]{% label format from numeric.bbx
        \printfield{labelprefix}%
        \printfield{labelnumber}}}
     {\setlength{\topsep}{0pt}% layout parameters from moderncvstyleclassic.sty
      \setlength{\labelwidth}{\hintscolumnwidth}%
      \setlength{\labelsep}{\separatorcolumnwidth}%
      \leftmargin\labelwidth%
      \advance\leftmargin\labelsep}%
      \sloppy\clubpenalty4000\widowpenalty4000}
  {\endlist}
  {\item}

\usepackage{etoolbox}
\makeatletter
\patchcmd{\makecvhead} % <cmd>
  {\ifthenelse{\isundefined{\@email}}{}{\makenewline\emailsymbol\emaillink\textcolor{grey}{\@email}}} % <search>
  {\ifthenelse{\isundefined{\@email}}{}{\makenewline{\emailsymbol\textcolor{grey}\emaillink{\@email}}}%
  } % <replace>
  {}{} % <success><failure>
\makeatother

\name{\textbf{Alexis}}{\color{orange}\textbf{TOUMI}}

\begin{document}

\hypersetup{
    pdftitle={CV-Alexis-TOUMI},
    urlcolor=orange,
    linkcolor=orange,
    citecolor=orange,
    pageanchor=false}

\makecvtitle

\vspace{-40pt}

{\centering
    \hypersetup{urlcolor=black}
    \homepagesymbol \href{https://alexis.toumi.xyz}{alexis.toumi.xyz}
    \hspace{25pt}
    \emailsymbol \href{mailto:alexis@toumi.email}{alexis@toumi.email}
    \hspace{25pt}
    30 avenue de Laumière, 75019 Paris, France
    \par}

\vspace{12pt}

\section{\textbf{EXPERIENCE}}

\cventry{2023 -- {\color{white} 2025}}{PlantingSpace}{R\&D Scientist}{}{}{
Developing our own blend of symbolic AI and Bayesian inference for program synthesis.
Applied category theory for explainable artificial intelligence and natural language processing.
}

\cventry{2019 -- 2024}{Quantinuum}{R\&D Scientist (part-time)}{}{}{
Pioneering quantum natural language processing and category theory for quantum ML.~\cite{ ToumiEtAl21a}\\
\emph{Software:} \href{https://discopy.org}{DisCoPy}, the Python toolkit for string diagrams (main author), \href{https://cqcl.github.io/lambeq/}{lambeq} (author).
}

\cventry{2022 -- 2023}{Laboratoire d'Informatique \& Syst\`emes}{Post-Doctoral Researcher}{}{}{
Formal methods for quantum cellular automata and distributed quantum computing.
}

\cventry{2022}{Le Lab Quantique}{General Manager}{}{}{
Administration of a French nonprofit that promotes the emergence of quantum technologies.
}

\cventry{2017 -- 2018}{Teklia \& IRHT (CNRS)}{Data Scientist}{}{}{Deep convolutional neural network for the layout analysis of pages from medieval manuscripts.
}

\cventry{2015 -- 2016}{Tinyclues}{Machine Learning Engineer (internship)}{}{}{
Tensor factorisation of complex relational data for email targeting on {\raise.17ex\hbox{$\scriptstyle\sim$}}100M users.
}

\cventry{2014 -- 2015}{Yonderlabs}{Data Scientist (internship)}{}{}{
Probabilistic graphical models for sentiment analysis, training my first neural word embedding.
}

\vspace{12pt}

\section{\textbf{EDUCATION}}

\cventry{2018 -- 2022}{University of Oxford}{D.Phil. Computer Science}{}{}{
\emph{Thesis:} ``Category Theory for Quantum Natural Language Processing''.\\
Wolfson Harrison UKRI Quantum Foundation \& Oxford-DeepMind Graduate Scholarship.
}

\cventry{2016 -- 2018}{University of Oxford}{M.Sc. Mathematics \& Computer Science}{}{Distinction}{
\emph{Thesis:} ``Categorical compositional distributional question, answer \& discourse analysis''.~\cite{CoeckeEtAl18b}
}

\cventry{2012 -- 2015}{University of Oxford}{B.Sc. Computer Science}{}{First-Class Honours}{
New College Scholarship. \emph{Thesis:} ``Equilibrium Checking in Reactive Modules Games''.~\cite{WooldridgeEtAl16}}

\vspace{12pt}

\printbibliography[title=\textbf{SELECTED PUBLICATIONS}]

\vspace{12pt}

\section{\textbf{LANGUAGES \& OTHER INTERESTS}}

\cvitem{Machine}{Python (native), Julia (fluent), Haskell (basic), Rust (beginner).}
\cvitem{Human}{French (native), English (fluent), German (basic), Arabic (beginner).}
\cvitem{Other}{Long-distance running, yoga, philosophy, history, cooking, coffee brewing, DJing.}

\end{document}
